### 2010-08-11 doc/tech_doc/a-rex/arex_tech_doc.tex
Adding description of %F substitution of a-rex
add preferredpattern option to allow ordering of replicas according to preference (bug 1933)

\item Download is initiated by the A-REX -- This is the case for files
  defined in the JD (with name and source). The A-REX alone is
  responsible to ensure that all required files will be available in
  the SD.\\ The supported protocols for sources at the moment are (in
  case of full installation): GridFTP, FTP, HTTP, HTTPS (HTTP over
  SSLv3). Some less standard sources and \emph{Indexing Services} are
  also supported, these are described in Section~\ref{sec:urls}. The
  A-REX fully relies on the HED framework~\cite{hed} for data
  transferring capabilities and so the actual set of supported
  protocols depends on the installed Data Management Components of the
  HED.

@@

@@

\begin{itemize}
\item [{\%R}] -- session root -- see command \emph{sessiondir}
\item [{\%C}] -- control dir -- see command \emph{control}
\item [{\%U}] -- username (as specified in configuration, hence empty for
'.' control directories)
\item [{\%u}] -- userid -- numerical
\item [{\%g}] -- groupid -- numerical
\item [{\%H}] -- home dir -- home of username as specified in /etc/passwd
\item [{\%Q}] -- default queue -- see command \emph{lrms}
\item [{\%L}] -- default lrms -- ses command \emph{lrms}
\item [{\%W}] -- installation path -- \$\{ARC\_LOCATION\}
\item [{\%c}] -- list of all control directories
\item [{\%I}] -- job ID (for plugins only, substituted in runtime)
\item [{\%S}] -- job state (for \emph{authplugin} plugins only, substituted
in runtime)
\item [{\%O}] -- reason (for \emph{localcred} plugins only, substituted
in runtime). Possible reasons are:
\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item [{new}] -- new job, new credentials
\item [{renew}] -- old job, new credentials
\item [{write}] -- write/delete file, create/delete directory
\item [{read}] -- read file, directory, etc.
\item [{extern}] -- call external program 
\end{list}
\end{itemize}

>>>>

\item Download is initiated by the A-REX -- This is the case for files
  defined in the JD (with name and source). The A-REX alone is responsible to
  ensure that all required files will be available in the SD.\\ The supported
  protocols for sources at the moment are (in case of full installation):
  GridFTP, FTP, HTTP, HTTPS (HTTP over SSLv3). Some less standard sources and
  \emph{Indexing Services} are also supported, these are described in
  Section~\ref{sec:urls}. In the case where a file in an indexing service
  resolves to multiple physical replicas, some selection of the ``best'' replica
  may be performed based on any available information on the access latency of
  those replicas. The A-REX fully relies on the HED framework~\cite{hed} for data
  transferring capabilities and so the actual set of supported protocols depends
  on the installed Data Management Components of the HED.

@@

\item \textbf{\textit{preferredpattern}}\textit{=pattern} - specifies
  a preferred pattern on which to sort multiple replicas of an input
  file. It consists of one or more patterns separated by a pipe
  character ($|$) listed in order of preference. Replicas will be
  ordered by the earliest match. If the dollar character (\$) is used
  at the end of a pattern, the pattern will be matched to the end of
  the hostname of the replica.

@@

\begin{itemize}
\item [{\%R}] -- session root -- see command \emph{sessiondir}
\item [{\%C}] -- control dir -- see command \emph{control}
\item [{\%U}] -- username (as specified in configuration, hence empty for
'.' control directories)
\item [{\%u}] -- userid -- numerical
\item [{\%g}] -- groupid -- numerical
\item [{\%H}] -- home dir -- home of username as specified in /etc/passwd
\item [{\%Q}] -- default queue -- see command \emph{lrms}
\item [{\%L}] -- default lrms -- ses command \emph{lrms}
\item [{\%W}] -- installation path -- \$\{ARC\_LOCATION\}
\item [{\%c}] -- list of all control directories
\item [{\%F}] -- path to configuration file of this instance
\item [{\%I}] -- job ID (for plugins only, substituted in runtime)
\item [{\%S}] -- job state (for \emph{authplugin} plugins only, substituted
in runtime)
\item [{\%O}] -- reason (for \emph{localcred} plugins only, substituted
in runtime). Possible reasons are:
\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item [{new}] -- new job, new credentials
\item [{renew}] -- old job, new credentials
\item [{write}] -- write/delete file, create/delete directory
\item [{read}] -- read file, directory, etc.
\item [{extern}] -- call external program 
\end{list}
\end{itemize}
